An investigation into the contentious phylogenetic results of the *Mixta* species

### 2021-04-24 Manuscript/Manuscript_Paper.Rmd
Update Manuscript_Paper.Rmd

## Spatial Patterns in the Closest Relatives from Genetic Distances
Circular plots were generated using the *Mixta* gene IDs to simulate their relative positions on the *Mixta* chromosomes and uncover positional and spatial patterns. The bars’ lengths and colours correspond to the species that was the closest relative to the *Mixta* gene at that position. The results between the two *Mixta* species for the closest relatives were the same except for one and two genes for the NTS and the AAS, respectively; therefore, only the results for *M. calida* are shown.

>>>>

## Spatial Patterns in the Closest Relatives from Genetic Distances
Circular plots were generated using the *Mixta* gene IDs to simulate their relative positions on the *Mixta* chromosomes and uncover positional and spatial patterns. The bars’ lengths and colours correspond to the species that was the closest relative to the *Mixta* gene at that position. The results between the two *Mixta* species for the closest relatives were the same except for one (*ttuB*) and two (*ttuB* and *secY*) genes for the NTS and the AAS, respectively; therefore, only the results for *M. calida* are shown.
